Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-05-27 Multiresolution_framework/ltx/manuscript.tex
corrected freq analysis

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & Spatial domain & n.a.\\
	$\mathbf{r}$ & Spatial location & [mm, mm]\\
	$t$ & Time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & Observation & mV\\
    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
	$h(t)$ & Post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline    
	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
	\hline                                                   
	$\phi_{j,l}(r)$&Scaling function&n.a\\
	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{State-Space Model}} \\
	\hline
		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
   	$\mathbf{C}$ & Observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$& spatial frequency  & cycles/mm \\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
	$\mathbf P^{f-}_t$, $\mathbf P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
	$\mathbf P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
	$\mathbf M_t$& Cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing

@@

where $c_i$ is the centre of the $i^{th}$ basis function of the kernel decomposition. Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}. With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel. This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined, since these are static functions. This has major computation advantages when solving the estimation problem. %\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field. } 

@@

where $i=\sqrt{-1}$. The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms. Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields

@@

	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}

>>>>

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & Spatial domain & n.a.\\
	$\mathbf{r}$ & Spatial location & [mm, mm]\\
	$t$ & Time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & Observation & mV\\
    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
	$h(t)$ & Post-synaptic response kernel & n.a.\\
	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline    
	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
	\hline                                                   
	$\phi_{j,l}(r)$&Scaling function&n.a\\
	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{State-Space Model}} \\
	\hline
		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&s, mV.spike$^{-1}$\\
   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
   	$\mathbf{C}$ & Observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$& spatial frequency  & cycles/mm \\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
	$\mathbf P^{f-}_t$, $\mathbf P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
	$\mathbf P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
	$\mathbf M_t$& Cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing

@@

where $c_i$ is the centre of the $i^{th}$ basis function of the kernel decomposition. Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}. With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel. This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined, since these are static functions. This has major computational advantages when solving the estimation problem. %\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field. } 

@@

where $\nu$ is the spatial frequency and $i=\sqrt{-1}$. The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms. Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields

@@

	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\frac{\pi in\nu}{2}).\label{eq:MRA-Wavelettransform}
